\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-28 journalWallFriction/Conclusion.tex
Text changes to improve readability

This paper presented techniques for controlling the positions of two particles using uniform inputs and non-slip boundary contact.  
The paper provided algorithms for precise position control. The algorithms relied on calculating reachable sets in a 2D $\Delta$ configuration space.
Extending Alg. \ref{alg:optimalAlg}  to 3D was straightforward, but increased the complexity.
Hardware experiments illustrated the algorithms in ex vivo and in artificial workspaces that mimic the geometry of biological tissue.

>>>>

This paper presented techniques for controlling the positions of two particles using uniform inputs and non-slip boundary contacts.  
The paper provided algorithms for precise position control. The algorithms relied on calculating reachable sets in a 2D $\Delta$ configuration space.
Extending Alg.~\ref{alg:optimalAlg}  to 3D was straightforward, but increased the complexity.
Hardware experiments illustrated the algorithms in ex vivo and in artificial workspaces that mimic the geometry of biological tissue.

### 2018-05-28 journalWallFriction/intro.tex
Text changes to improve readability

\begin{figure}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{firstpicLeft.pdf}\put(28,-10){workspace}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{magneticsetup.pdf}\put(28,-8){magnetic setup}\end{overpic}
\vspace{1em}
\caption{\label{fig:IntroPic}
Workspace and magnetic setup for an experiment of positioning particles that receive the same control inputs, but cannot move while a control input pushes them into a boundary.
} \vspace{-1em}
\end{figure}
%\todo{add the picture of magnetic setup}

>>>>

\begin{figure}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{firstpicLeft.pdf}\put(28,-10){workspace}\end{overpic}
\begin{overpic}[width=0.45\columnwidth]{magneticsetup.pdf}\put(28,-8){magnetic setup}\end{overpic}
\vspace{1em}
\caption{\label{fig:IntroPic}
Workspace and magnetic setup for an experiment to position particles that receive the same control inputs, but cannot move while a control input pushes them into a boundary.
} \vspace{-1em}
\end{figure}
%\todo{add the picture of magnetic setup}

### 2018-05-28 journalWallFriction/simulation.tex
Edited one caption.
Text changes to improve readability

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{deltanum.pdf}\end{overpic}\\
%\vspace{1em}
\begin{overpic}[width=\columnwidth]{deltadist.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:deltanumdist}
The worst case path length occurs when particles must swap antipodes. This can never be achieved but can be asymptotically approached. Plot shows decreasing error as the number of moves grows.
} 
\end{figure}

@@

\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of particles $1$ and $2$ and goal position of particle $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The bottom row shows the number of moves required for the same configurations.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. 
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

The path length grows when the goals have $\pi$ difference and are very close to the boundary.  The worst case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Fig.~\ref{fig:contourPlots} shows the same concepts in a square workspace. Fig.~\ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. All of the discussed plots have considered the particles to be unique. If particles are interchangeable and it does not matter to put the specific particle to its goal location, the path length will be significantly smaller. The bottom row of  Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles.

 %If the length of each side of the square workspace is $L$, the worst case path length is $(\sqrt{2}+2)L$.

>>>>

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{deltanum.pdf}\end{overpic}\\
%\vspace{1em}
\begin{overpic}[width=\columnwidth]{deltadist.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:deltanumdist}
The worst-case path length occurs when particles must swap antipodes. This can never be achieved but can be asymptotically approached. Plot shows decreasing error as the number of moves grows.
} 
\end{figure}

@@

\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of particles $1$ and $2$ and goal position of particle $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The middle row shows the number of moves required for the same configurations. The bottom row shows the same configuration but when the particles are interchangeable.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. 
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

The path length grows when the goals have $\pi$ difference and are very close to the boundary.  The worst-case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Fig.~\ref{fig:contourPlots} shows the same concepts in a square workspace. Fig.~\ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. 
 Thus far, this paper has considered the particles to be unique. If particles are interchangeable, the path lengths often decrease. The bottom row of  Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles. The worst-case path lengths decrease by ??\%, ??\%, and ??\% for the three test cases shown. %TODO: shiva, insert numbers.

 %If the length of each side of the square workspace is $L$, the worst-case path length is $(\sqrt{2}+2)L$.

### 2018-05-28 journalWallFriction/theory2robAlgs.tex
Text changes to improve readability

\vspace{-0.75em}
{
\begin{overpic}[width =\figwid]{storyWorst1.pdf}\put(60,10){Move 1}
\put(10,85){f)}
\put(15,10){$s_1,g_2$}
\put(65,88){$s_2,g_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst2.pdf}\put(60,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst4.pdf}\put(60,10){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst6.pdf}\put(60,10){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst7.pdf}\put(60,10){Move 5}
\put(15, 85){worst case}\put(15,75){path length}\put(15, 62){$(\sqrt{2}+2)L$}
\end{overpic}
}\\

@@

The $\Delta$ configuration space is a set of all possible $\Delta p$ values.
 $\Delta$ configuration spaces for a representative set of workspaces are shown in Fig.~\ref{fig:polygon}. The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first.
 Fig.~\ref{fig:regionMove} shows the starting and ending relative positions as $\Delta s$ and $\Delta g$ in the $\Delta$ configuration space.  The next subsections give procedures to compute the 2-move reachable set.% in Fig.~\ref{fig:regionMove}.% The reachable set is the part of $\Delta$ configuration space where if one particle touches a wall in a specific location, the other particle can make the required relative distance without causing the touching particle to move. We will discuss how to make reachable sets in the next subsections.

@@

  \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{reachable sets} are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the reachable set, we define a temporary goal, $\Delta g_c$, which is the closest point on the reachable set to $\Delta g$ and apply two moves that make the relative position closer to $\Delta g$. We do it until we reach the relative goal position.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}
 Algorithm ~\ref{alg:optimalAlg} first computes the 2-move reachable set. If the goal relative position is in the reachable set, we move particles to achieve that relative position. If it is not in the reachable set, we move particles to achieve the closest point on the reachable set from $\Delta g$. 
>>>>>>> Stashed changes
 \emph{Achieving} a $\Delta$ configuration requires two-moves, the first to move until one particle touches a wall, and the second to adjust the relative spacing.
 Once the correct \emph{relative} position has been achieved, a final translation delivers both particles to their goal destinations. %we go to the final goal position. If it is not our final goal, 
 Otherwise, we iterate until we reach the goal. 
\begin{algorithm}[htb]
\caption{ { \sc 2-ParticlePathPlanning}($s_1,s_2,g_1,g_2,P,\epsilon$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
%$(0,0)$ is bottom corner,
 $P$ is a description of the workspace. $\epsilon$ is a positive error bound.
% \emph{PathList} contains all the paths sorted by their path length plus an admissible heuristic. 
% \State  \emph{PathList} $\gets \{\}$
 \State $(p_1,p_2) \gets (s_1,s_2) $ \Comment $p_1 , p_2$ are current positions
\State  moves $\gets \{\}$
% \State $R \gets   \{ p_1,p_2,g_1,g_2  ,\textrm{moves}\} $ \Comment $R$ contains the current particle positions, the goal positions, and the move sequence
 \State $\Delta p \gets p_2-p_1$
 \State $\Delta g \gets g_2-g_1$
\While {$||\Delta p - \Delta g|| > \epsilon$}  %R.p_1 \ne g_1$ \textbf{and} $R.p_2 \ne g_2$}
\State $R_{\textrm{SET}}\gets$  Compute 2-move reachable set  \Comment use Alg.~\ref{alg:polygonReachbale} or \ref{alg:circularReachbale}
\State $ \Delta g_c\gets $nearest point in $R_{\textrm{SET}}$ to $\Delta g$
\State $m \gets $move-to-wall corresponding to $\Delta g_c$
\State moves $\gets$ Append $m$ to moves
\State $(p_1, p_2)$ $\gets$ ApplyMove $m$ to $(p_1,p_2)$
%\State $p_2$ = ApplyMove($p_2,m$)
 \State $\Delta p \gets p_2-p_1$
\EndWhile
\State moves $\gets$ Append $g_2-p_2$ to moves \Comment translate to goal
\State \Return moves
\end{algorithmic}
\end{algorithm}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{$\Delta$ Configuration Space}

% $\Delta$ configuration space is a space containing all the possible relative distances for $p_1$ and $p_2$. 
Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is a $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided. 
 To give an intuition, suppose that the first particle is positioned on a vertex of the workspace. The $\Delta$ configuration space is mainly determined by moving the second particle along the edges of the workspace and considering its relative distance to the first particle.
%  what $\Delta$ configuration space is, consider the first particle on a vertex of the workspace. Now if the other particle moves on the boundary of the workspace, the relative distance between the two particles is maximized. 
In particular, to generate the $\Delta$ configuration space we iterate through all vertices $v_i$.  %In each iteration, we put the first particle at the $i^{\textrm{th}}$ vertex. 
At each iteration, we compute $v_i - v_j$  ($1 \leq j \leq n$) and then make an $n$-sided polygon according to these values. Since our current workspaces are convex, the convex hull of these  $n$-sided polygons determines the boundary of the $\Delta$ configuration space. To give a concrete example, Fig.~\ref{fig:irregular} shows an arbitrary 4-sided workspace on the left. All the 4-sided polygons made by the computation of $(v_i-v_j)$s are shown in the middle and accordingly, $\Delta$ configuration space is shown on the right with 2-move reachable sets drawn in transparent blue. We will discuss how to generate 2-step reachable sets in the following subsection.

@@

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets} are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal, $\Delta g_c$, which is the closest point on the 2-move reachable set to $\Delta g$ and apply two moves that make the relative position closer to $\Delta g$. We do it until we reach the relative goal position.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}
 Fig. \ref{fig:polygon} shows different workspaces and their representative $\Delta$ configuration spaces.

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(17,-3){\small{Generates polygon defined by $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $i,i+1$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
If a particle is touching a wall, the other particle can move freely in the reachable set as shown in Fig.~\ref{fig:TwoRegions}.
Alg.~\ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
 Fig.~\ref{fig:polygonAlg} illustrates the procedure to construct the 2-move reachable set generated by collisions with the $i^{\textrm{th}}$ side.
 % $\overline{ s_1s_2 }\nparallel \overline{ p_i p_{i+1}} $
  If one particle hits side $i$ before the other (one particle will always hit before the other unless  the particles are parallel to the wall), the 2-move reachable set is defined by a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
 % by computing the reachable set for all the sides of the polygon. Fig.~\ref{fig:polygonAlg} shows different cases with the particles and an arbitrary side. If particle 2 is touching the $i^{th}$ side, we compute if particle 1 will stay in the polygon or not. Then we generate the reachable set using all the vertices of the polygon and potential place of particle 1. We unify all the reachable sets corresponding to all the sides. Alg.~\ref{alg:polygonReachbale} computes reachable set for any convex polygonal workspace. 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Top row shows a polygonal workspace with its 2-move reachable sets. Bottom row, left circle shows the workspace. %, and the corresponding reachable set when blue robot is touching the wall is shown as a blue region. 
Right shows the $\Delta$ configuration space and the 2-move reachable set that is shown in red is representative of the point we need to go to get to the goal relative distance in one move.%representative of the blue and pink reachable sets shown in the workspace.
}
\end{figure*}
To compute the 2-move reachable set for a circular workspace, first we consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the workspace.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.

>>>>

\vspace{-0.75em}
{
\begin{overpic}[width =\figwid]{storyWorst1.pdf}\put(60,10){Move 1}
\put(10,85){f)}
\put(15,10){$s_1,g_2$}
\put(65,88){$s_2,g_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst2.pdf}\put(60,10){Move 2}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst4.pdf}\put(60,10){Move 3}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst6.pdf}\put(60,10){Move 4}
\end{overpic}
\begin{overpic}[width =\figwid]{storyWorst7.pdf}\put(60,10){Move 5}
\put(15, 85){worst-case}\put(15,75){path length}\put(15, 62){$(\sqrt{2}+2)L$}
\end{overpic}
}\\

@@

The $\Delta$ configuration space is a set of all possible $\Delta p$ values.
 $\Delta$ configuration spaces for a representative set of workspaces are shown in Fig.~\ref{fig:polygon}. 
  The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first.
 Fig.~\ref{fig:polygon} shows the starting and ending relative positions as $\Delta s$ and $\Delta g$ in the $\Delta$ configuration space.  The next subsections give procedures to compute the 2-move reachable set.% in Fig.~\ref{fig:regionMove}.% The reachable set is the part of $\Delta$ configuration space where if one particle touches a wall in a specific location, the other particle can make the required relative distance without causing the touching particle to move. We will discuss how to make reachable sets in the next subsections.

@@

 Algorithm ~\ref{alg:optimalAlg} first computes the 2-move reachable set. If the goal relative position is in the reachable set, we move particles to achieve that relative position. If it is not in the reachable set, we move particles to achieve the closest point on the reachable set from $\Delta g$. 
 \emph{Achieving} a $\Delta$ configuration requires two-moves, the first to move until one particle touches a wall, and the second to adjust the relative spacing.
 Once the correct \emph{relative} position has been achieved, a final translation delivers both particles to their goal destinations. %we go to the final goal position. If it is not our final goal, 
 Otherwise, we iterate until we reach the goal. 
\begin{algorithm}[htb]
\caption{ { \sc 2-ParticlePathPlanning}($s_1,s_2,g_1,g_2,P,\epsilon$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
%$(0,0)$ is bottom corner,
 $P$ is a description of the workspace. $\epsilon$ is a positive error bound.
% \emph{PathList} contains all the paths sorted by their path length plus an admissible heuristic. 
% \State  \emph{PathList} $\gets \{\}$
 \State $(p_1,p_2) \gets (s_1,s_2) $ \Comment $p_1 , p_2$ are current positions
\State  moves $\gets \{\}$
% \State $R \gets   \{ p_1,p_2,g_1,g_2  ,\textrm{moves}\} $ \Comment $R$ contains the current particle positions, the goal positions, and the move sequence
 \State $\Delta p \gets p_2-p_1$
 \State $\Delta g \gets g_2-g_1$
\While {$||\Delta p - \Delta g|| > \epsilon$}  %R.p_1 \ne g_1$ \textbf{and} $R.p_2 \ne g_2$}
\State $R_{\textrm{SET}}\gets$  Compute 2-move reachable set  \Comment use Alg.~\ref{alg:polygonReachbale} or \ref{alg:circularReachbale}
\State $ \Delta g_c\gets $nearest point in $R_{\textrm{SET}}$ to $\Delta g$
\State $m \gets $move-to-wall corresponding to $\Delta g_c$
\State moves $\gets$ Append $m$ to moves
\State $(p_1, p_2)$ $\gets$ ApplyMove $m$ to $(p_1,p_2)$
%\State $p_2$ = ApplyMove($p_2,m$)
 \State $\Delta p \gets p_2-p_1$
\EndWhile
\State moves $\gets$ Append $g_2-p_2$ to moves \Comment translate to goal
\State \Return moves
\end{algorithmic}
\end{algorithm}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{$\Delta$ Configuration Space}
% ANOTHER TRY
The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. 
The  $\Delta$ configuration space for an $n$-sided convex polygon $P$ can be constructed by translating $n$ copies of $P$  so that each copy moves a different vertex of $P$ to $(0,0)$.
Because $P$ is convex, the convex-hull of all these translated vertices is the boundary of the  $\Delta$ configuration space.
 For an $n$-sided convex polygon, the $\Delta$ configuration space is a $2n$-sided convex polygon.
  Even-sided regular polygons are a special case in which half the sides align and the $\Delta$ configuration space is $n$-sided. 
An example $\Delta$ configuration space construction is shown in Fig.~\ref{fig:irregular}: 
a four-sided workspace is on the left, 
the four translated copies with dashed lines outlining the convex hull is in the middle,
 and the resulting $\Delta$ configuration space is on the right.  
 The 2-move reachable sets for the given $\Delta$s starting configuration are drawn in transparent blue.
The following subsection describes how 2-move reachable sets are constructed.

% ORIGINAL
%Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is a $2n$-sided convex polygon.
% A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided. 
% To give an intuition, suppose that the first particle is positioned on a vertex of the workspace. The $\Delta$ configuration space is mainly determined by moving the second particle along the edges of the workspace and considering its relative distance to the first particle.
%In particular, to generate the $\Delta$ configuration space we iterate through all vertices $v_i$.  %In each iteration, we put the first particle at the $i^{\textrm{th}}$ vertex. 
%At each iteration, we compute $v_i - v_j$  ($1 \leq j \leq n$) and then make an $n$-sided polygon according to these values. Since our current workspaces are convex, the convex hull of these  $n$-sided polygons determines the boundary of the $\Delta$ configuration space. To give a concrete example, Fig.~\ref{fig:irregular} shows an arbitrary 4-sided workspace on the left. All the 4-sided polygons made by the computation of $(v_i-v_j)$s are shown in the middle and accordingly, $\Delta$ configuration space is shown on the right with 2-move reachable sets drawn in transparent blue. We will discuss how to generate 2-step reachable sets in the following subsection.

@@

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets}, are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal $\Delta g_c$ (the closest point on the 2-move reachable set to $\Delta g$) and apply two moves to achieve $\Delta g_c$. We repeat this process until the relative goal position is achieved.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(17,-3){\small{Generates polygon defined by $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $i,i+1$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Fig. \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
  The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Alg.~\ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace.
  If one particle hits edge $i$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $i^{\textrm{th}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each the move 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}
To compute the 2-move reachable set for a circular workspace, first consider all possible first contact locations.
 The set of boundary points that a particle can touch before the  other particle  touches is an arc of angle $2(\pi - \frac{\arcsin{d_{12}}}{r})$, where $d_{12}= ||s_1 - s_2||$ and $r$ is the radius of the workspace.
 %Here $\alpha$ is the arc of the circle that it is not possible to keep the current relative distance while one robot is touching the wall in that point and is defined by $\alpha = 2 \sin ^{-1}(d)$. 
 We define the angle between two particles as $\theta = \arctan(\frac{p_1.x-p_2.x}{p_1.y - p_2.y})$.
